Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-30 draft/paper1_jenny.tex
Edit 1-D profile

\def\m2l{{$M_{\star}/L_{\star}$}}
\def\mden{{$\mu_{\star}$}}

@@

    Meanwhile, in the outskirts, we can notice significant differences where more 
    massive galaxies have gradually more flattened \mden{} profiles and show more 
    prominent stellar halos.
    It is also interesting to see that the distributions of \mden{} profiles show 
    considerably large scatter at large radius. 
    Given the \s2n{} of the HSC image at these surface brightness levels, these 
    scatters should reflect the \textbf{intrinsic scatter of the structures of 
    massive galaxies in their stellar halos}.
    Overall, the structures of massive galaxies are \emph{clearly not self-similar}
    out to 100 kpc. 
    Some of our \mden{} profiles show signs of unphysical truncation and fluctuation 
    related to inaccurate sky subtraction. 
    In this paper, we do not use profiles beyond 100 kpc, even though the median 
    \mden{} profiles for the two most massive bins behave reasonably out to 
    ${\sim} 200$ kpc.

    The right panel of Fig~\ref{fig:avg_prof} compares our results with previous 
    works. 
    Most previous studies have relied on stacking techniques to measure surface 
    brightness profiles out to large radii.
    So far, the surface brightness profiles of massive galaxies out to such large 
    radii was mostly derived via image stacking technique that suffers from several 
    systematic issues (e.g. \citealt{Tal2011, DSouza2015}; but also see:
    \citealt{Capaccioli2015}); and the \mden{} profiles are even more rarely 
    available.

    \citet{Huang2013a} derived \mden{} profiles for a small sample of very nearby 
    ellipticals (within 100 Mpc; median \logms{} ${\sim} 11.3$ based on shallower 
    images) from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}). 
    Because this is a very low redshift sample, these profiles are robust to smaller scales, $r=1$ kpc. 
    The \citet{Huang2013a} profiles show good agreement with ours in the region of 
    overlap and out to 50 kpc. 
    CGS images are deeper than SDSS images in the $r$-band, but the median 
    profile from \citet{Huang2013a} still only reaches ${\sim} 50$ kpc for $z{\sim} 0$ 
    massive galaxies.
    Meanwhile, our deep HSC images can reliably deliver individual \mden{} profiles 
    for $z{\sim} 0.4$ galaxies out to at least 100 kpc.

>>>>

\def\m2l{{$M_{\star}/L_{\star}$}}
\def\s2n{{$\mathrm{S}/\mathrm{N}$}}
\def\mden{{$\mu_{\star}$}}

@@

    Meanwhile, in the outskirts, we can notice significant differences where more 
    massive galaxies have gradually more flattened \mden{} profiles and show more 
    prominent stellar halos.
    It is also interesting to see that the distributions of \mden{} profiles show 
    considerably large scatter at large radius. 
    Given the \s2n{} of the HSC image at these surface brightness levels, these 
    scatters should reflect the \textbf{intrinsic scatter of the structures of 
    massive galaxies in their stellar halos}.
    Overall, the structures of massive galaxies are \textbf{clearly not 
    self-similar} out to 100 kpc. 
    Some of our \mden{} profiles show signs of unphysical truncation and fluctuation 
    related to inaccurate sky subtraction. 
    In this paper, we do not use profiles beyond 100 kpc, even though the median 
    \mden{} profiles for the two most massive bins behave reasonably out to 
    ${\sim} 200$ kpc.

    The right panel of Fig~\ref{fig:avg_prof} compares our results with several 
    previous works. 
    So far, deep \mden{} profiles of massive galaxies are rarely available. 
    Even in the nearby universe, it is still not easy to reach to the very outskirt
    of massive galaxy due to several technical issues (e.g. 
    \citealt{Capaccioli2015, Iodice2016, Iodice2017, Spavone2017, Mihos2017})

    Although it is relative easier to reach to the very outskirt of massive galaxy 
    in the nearby universe, the small volume limits the number of available 
    galaxies at high-mass end. 
    Most previous studies often focus more on the surface brightness profiles, 
    and they also depend on stacking techniques or model-dependent method to 
    study the structure of massive galaxies in their outskirts.

    Most previous studies have relied on stacking techniques to measure surface 
    brightness profiles out to large radii.
    So far, the surface brightness profiles of massive galaxies out to such large 
    radii was mostly derived via image stacking technique that suffers from several 
    systematic issues (e.g. \citealt{Tal2011, DSouza2015}; but also see:
    \citealt{Capaccioli2015}); and the \mden{} profiles are even more rarely 
    available.

    \citet{Huang2013a} derived \mden{} profiles for a small sample of very nearby 
    ellipticals (within 100 Mpc; median \logms{} ${\sim} 11.3$ based on shallower 
    images) from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}). 
    Because this is a very low redshift sample, these profiles are accurate to 
    smaller scales, $r=1$ kpc. 
    The \citet{Huang2013a} profiles show good agreement with ours in the region of 
    overlap and out to 50 kpc. 
    CGS images are deeper than SDSS images in the $r$-band, but the median 
    profile from \citet{Huang2013a} still only reaches ${\sim} 50$ kpc for $z{\sim} 0$ 
    massive galaxies.
    Meanwhile, our deep HSC images can reliably deliver individual \mden{} profiles 
    for $z{\sim} 0.4$ galaxies out to at least 100 kpc.
